Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-10 edubots_surveys.Rnw
review survey validation

To avoid any kind of bias and to ensure the quality of the questionnaire, a panel board was consulted. There were three questions for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
Clarity was measured as an answer to the question: Is the item well presented and without ambiguity? \footnote{Original text: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: Yes or No.
Both Importance and Adequateness were measured in a Likert scale from 1 to 4 (1 low, 4 high).

The panel board was composed by 7 volunteer experts that have wide experience as educators and researchers. The results obtained are summarized in Table \ref{tab:validation}.

As validation shows, all expert agree without any doubt about the clarity of each question. Furthermore, there is a large consensus regarding the Importance and Adequateness of all the eight questions in the questionnaire.

>>>>

To avoid any kind of bias and to ensure the quality of the questionnaire, a panel of experts was consulted. The panel board evaluated three aspects for each item of the questionnaire: Clarity, Importance, and Adequateness.
Clarity was measured as an answer to the question: ``Is the item well presented and without ambiguity?" \footnote{Original text in Spanish: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: ``Yes" or ``No".
Both Importance and Adequateness were measured on a Likert scale from 1 to 4 (1 being low and 4 being high).

The panel board was composed of 7 volunteer experts that have wide experience as educators and researchers. The results obtained are summarized in Table \ref{tab:validation}.

As validation shows, all experts agree without any doubt about the clarity of each question. Furthermore, there is a large consensus regarding the Importance and Adequateness of all eight questions in the questionnaire.
